Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-13 paper/main.tex
working on results section:   - exploring individual differences in links between feature clustering, accuracy, and temporal clustering on early and late lists in the order manipulation conditions  - added a new barplot to more directly illustrate group-level trends  - also added some across-condition stats
Note: i haven't yet added the new stats to the text

>>>>

\begin{figure}[tp] \centering
    \includegraphics[width=0.7\textwidth]{figures/memory_perf_barchart_compare}

\caption{\textbf{Recall probability and clustering scores on early and late
lists.} The bar heights display the average (across participants) recall
probabilities (\textbf{A.}), temporal clustering scores (\textbf{B.}), and
feature clustering scores (\textbf{C.}) for early (gray) and late (gold) lists.
For the feature rich bars (left), the feature clustering scores are averaged
across features. For the order manipulation conditions, feature clustering
scores are displayed for the focused-on feature for each condition (e.g.,
category clustering scores are displayed for the category condition, and so
on). All panels: error bars denote bootstrap-estimated 95\% confidence
intervals. The horizontal dotted lines denote the average values (across all
lists and participants) for the feature rich condition.
\textbf} \label{fig:barplots}
